---
title: "Communication with DaVinci Modules"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{communication}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette demonstrates how DaVinci modules can communicate with each other within a single application. Specifically, it shows how the spider-plot module can send a selected patient ID to the patient-profile module, allowing users to jump directly from a data point in the spider plot to a detailed profile view of that patient.

```{r papo, eval=FALSE}
papo_mod <- dv.papo::mod_patient_profile(
  module_id = "mod_papo",
  subject_level_dataset_name = "adsl",
  subjid_var = "USUBJID",
  sender_ids = "mod_spider",
  summary = list(
    vars = c("USUBJID", "AGE", "SEX", "ARM"),
    column_count = 2
  )
)
```

To enable navigation from the spider plot to the patient profile, the app creator simply sets `receiver_id = "mod_papo"` in the spider plot module’s configuration.

```{r demo, eval=FALSE}
dv.manager::run_app(
  data = list(
    "Demo" = list(adsl = adsl, adtr = adtr)
  ), 
  module_list = list(
    "Spider Plot" = spiderplot_mod,
    "Patient Profile" = papo_mod
  ),
  title = "Spider Plot Demo",
  filter_data = "adsl",
  filter_key = "USUBJID",
  filter_type = "datasets"
)
```
