---
title: "Module Customization"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{customization}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dv.spiderplot)
```

This vignette explains the customization options available in the `mod_spiderplot()` function. Each section focuses on a specific parameter (or group of related parameters) and shows how it affects the plot and the interactive controls available to end users.

For a general introduction to the module — including data preparation and how to launch the application — see `vignette("dv-spiderplot")`.

## Data Setup

The examples below use CDISC ADaM-compliant datasets from the `pharmaverseadam` package. 

```{r data}
adsl <- pharmaverseadam::adsl
adtr <- pharmaverseadam::adtr_onco |>
  dplyr::mutate(
    ARM    = factor(ARM, levels = c("Placebo", "Xanomeline Low Dose", "Xanomeline High Dose")),
    SEX    = factor(SEX, levels = c("F", "M"), labels = c("Female", "Male")),
    AVISIT = forcats::fct_reorder(AVISIT, AVISITN)
  )

attr(adtr[["ARM"]], "label") <- "Planned Arm"
attr(adtr[["SEX"]], "label") <- "Sex"
attr(adtr[["AVISIT"]], "label") <- "Analysis Visit"

attr(adsl, "meta") <- list(mtime = Sys.time())
attr(adtr, "meta") <- list(mtime = Sys.time())
```

## Variable Selection

**Parameters:** `x_vars`, `y_vars`

Supply a character vector to `x_vars` and `y_vars` to define which variables end users can select for the x- and y-axes. 

```{r var-selection}
spiderplot_mod <- mod_spiderplot(
  module_id = "mod_spider",
  subject_level_dataset_name = "adsl",
  results_dataset_name = "adtr",
  subjid_var = "USUBJID",
  x_vars = c("ADY", "AVISIT"),
  y_vars = c("PCHG", "CHG")
)
```


## Color Grouping

**Parameters:** `color_vars`, `color_palette`

Set `color_vars` to expose a **Color Variable** dropdown in the Plot Options panel. The variables listed in `color_vars` must exist in the **subject-level** dataset.

```{r color-vars}
spiderplot_mod <- mod_spiderplot(
  module_id = "mod_spider",
  subject_level_dataset_name = "adsl",
  results_dataset_name = "adtr",
  subjid_var = "USUBJID",
  x_vars = c("ADY", "AVISIT"),
  y_vars = c("PCHG", "CHG"),
  color_vars = c("ARM", "SEX")
)
```

Use `color_palette` to map specific factor levels to colors. The palette must be a **named character vector** where names are factor level values and values are color strings.

```{r color-palette}
spiderplot_mod <- mod_spiderplot(
  module_id = "mod_spider",
  subject_level_dataset_name = "adsl",
  results_dataset_name = "adtr",
  subjid_var = "USUBJID",
  x_vars = c("ADY", "AVISIT"),
  y_vars = c("PCHG", "CHG"),
  color_vars = c("ARM", "SEX"),
  color_palette = c(
    "Placebo" = "#E41A1C",
    "Xanomeline Low Dose" = "#377EB8",
    "Xanomeline High Dose" = "#4DAF4A"
  )
)
```


## Faceting

**Parameters:** `facet_rows`, `facet_cols`

Faceting splits the spider plot into a grid of sub-plots. Set `facet_rows` to define the row dimension and `facet_cols` for the column dimension.

```{r faceting}
spiderplot_mod <- mod_spiderplot(
  module_id  = "mod_spider",
  subject_level_dataset_name = "adsl",
  results_dataset_name = "adtr",
  subjid_var = "USUBJID",
  x_vars = c("ADY", "AVISIT"),
  y_vars = c("PCHG", "CHG"),
  facet_rows = c("SEX"),
  facet_cols = c("AGEGR1", "ARM")
)
```


## Plot Dimensions

**Parameters:** `height_default`, `height_range`

The plot height is exposed to users via a **Height** slider in the Plot Options panel. Two parameters control it:

- `height_default` sets the initial slider value in inches
- `height_range` sets the `c(min, max)` bounds of the slider

```{r dimensions}
spiderplot_mod <- mod_spiderplot(
  module_id = "mod_spider",
  subject_level_dataset_name = "adsl",
  results_dataset_name = "adtr",
  subjid_var = "USUBJID",
  x_vars = c("ADY", "AVISIT"),
  y_vars = c("PCHG", "CHG"),
  height_default = 6,
  height_range = c(4, 8)
)
```

## Plot Title and Subtitle

**Parameters:** `title`, `subtitle`

A static title and subtitle can be set for the plot. These are fixed at module configuration time and cannot be changed by the user at runtime.

```{r labels}
spiderplot_mod <- mod_spiderplot(
  module_id = "mod_spider",
  subject_level_dataset_name = "adsl",
  results_dataset_name = "adtr",
  subjid_var = "USUBJID",
  x_vars = c("ADY", "AVISIT"),
  y_vars = c("PCHG", "CHG"),
  title = "Tumor Size Change Over Time",
  subtitle = "Study CDISC-PILOT-01"
)
```
